Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-08 paper/main.tex
[issue 2.25] combine sdss calibration curves

\begin{figure*}
  \centering
  \begin{minipage}[c]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/sdss_calibration_conv.pdf}
    \caption{Calibration curve for ConvNet as applied to the SDSS data set.}
    \label{fig:sdss_calibration_conv}
  \end{minipage}
  \hfill
  \begin{minipage}[c]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/sdss_calibration_tpc.pdf}
    \caption{Calibration curve for $\rmn{TPC}_{\rmn{morph}}$
      as applied to the SDSS data set.}
    \label{fig:sdss_calibration_tpc}
  \end{minipage}
\end{figure*}

@@

Figures~\ref{fig:sdss_calibration_conv} and \ref{fig:sdss_calibration_tpc}
show the calibration curves of ConvNet and $\rmn{TPC}_{\rmn{morph}}$,
respectively.
The calibration curve of ConvNet in Figure~\ref{fig:sdss_calibration_conv}
is not as well-calibrated as the calibration curve in
Figure~\ref{fig:clens_calibration_conv},
where the same ConvNet model was applied to the CFHTLenS data set.
However, ConvNet may still be better calibrated than $\rmn{TPC}_{\rmn{morph}}$,
even when it is applied to the SDSS data set.
Although it is not straightforward to compare the two calibration curves by
visual inspection, Table~\ref{table:sdss_metrics} shows that the CAL metric of
ConvNet is lower than that of $\rmn{TPC}_{\rmn{morph}}$.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{figures/sdss_calibration.pdf}
  \caption{
    \changed{
    Calibration curves for ConvNet (red) and $\rmn{TPC}_{\rmn{morph}}$
    (blue) as applied to the SDSS data set.
    }
    }
  \label{fig:sdss_calibration}
\end{figure}

@@

\changed{
Figure~\ref{fig:sdss_calibration} shows
the calibration curves of ConvNet and $\rmn{TPC}_{\rmn{morph}}$.
}
The calibration curve of ConvNet in Figure~\ref{fig:sdss_calibration}
is not as well-calibrated as the calibration curve in
Figure~\ref{fig:clens_calibration_conv},
where the same ConvNet model was applied to the CFHTLenS data set.
However, ConvNet may still be better calibrated than $\rmn{TPC}_{\rmn{morph}}$,
even when it is applied to the SDSS data set.
Although it is not straightforward to compare the two calibration curves by
visual inspection, Table~\ref{table:sdss_metrics} shows that the CAL metric of
ConvNet is lower than that of $\rmn{TPC}_{\rmn{morph}}$.
